Preventing runtime errors of Redis at compile time

### 2015-11-17 paper.tex
5. Making Redis polymorphic

Although everything in Redis is essentially a binary string, they are treated
differently. Redis supports many different kind of data structures, such as
strings, hashes, lists, etc. These values are of different data types, and some
commands only work on certain types of them, much like how language C treats
a piece of data.

@@

\section{Type-level Dictionary}

@@

\subsection{Datatype promotion}
Normally, at the term level, we could express data type of the dictionary with
\emph{type synonym} like this.\footnotemark

@@

\section{Indexed Monad}

@@

\subsection{The first attempt}

@@

\section{Bookkeeping with type families}
\subsection{Closed type families}

@@

% \begin{minted}[xleftmargin=1em]{haskell}
% Get '['("ha", Int)]
% \end{minted}

%  are
% permitted as well.
%
%
%  open type synonym families, and
% closed type synonym families
% One of which is to compute types, we are using closed type families, since all
% we want is to use it as a function on the type level, no extensibility needed,
% everything is defined in one-piece

%
% \mintinline{haskell}{IMonad} \mintinline{haskell}{IMonad} takes three arguments: an intitial state \mintinline{haskell}{p}, a final
%  state, and computes a value of type a

\subsection{Proxies and Kind polymorphism}

% Since Haskell has a phase distinction\cite{phasedistinction} between
%
% To link a symbol with a term-level value
%
% What we need is a \emph{singleton}\cite{singletons}, a type
% that has only one instance at the term level.

% With \emph{kind polymorphism}\cite{promotion}, we have parametric polymorphism
% at the kind level.

\begin{minted}[xleftmargin=1em]{haskell}
Proxy :: Proxy "a"
\end{minted}

\subsection{Closed type families}

\subsection{Conclusions and Related Work}

>>>>

Although everything in Redis is essentially a binary string, they are treated
differently. Redis supports many different kind of data structures, such as
strings, hashes, lists, etc. These values have different datatypes, and most
commands only work with certain types of them, much like how C language treats
a piece of data.

@@

\section{Type-level dictionaries}

@@

\subsection{Datatype promotion}
Normally, at the term level, we could express the datatype of dictionary with
\emph{type synonym} like this.\footnotemark

@@

\section{Indexed monads}

@@

\subsection{\mintinline{text}{PING}: the first attempt}

@@

\section{Type-level functions}
\subsection{Closed type families}

@@

\subsection{Proxies and singleton types}

With functions on dictionaries, now we could annotate the effects of a command
in types. \mintinline{text}{DEL} removes a key from the current database,
regardless of its type.

\begin{minted}[xleftmargin=1em]{haskell}
del :: KnownSymbol s
    => Proxy s
    -> Edis xs (Del xs s) (Either Reply Integer)
del key = Edis $ Hedis.del (symbolVal key)
\end{minted}

\mintinline{haskell}{KnownSymbol} is a class that gives the string associated
with a concrete type-level symbol, which can be retreived with
\mintinline{haskell}{symbolVal}.\footnotemark

\footnotetext{They are defined in \mintinline{haskell}{GHC.TypeLits}.}

Since Haskell has a \emph{phase distinction}\cite{phasedistinction}, types are
erased before runtime. It's impossible to obtain informations directly from
types, we can only do this indirectly, with \emph{singleton types}
\cite{singletons}.

A singleton type is a type that has only one instance, and the instance can be
think of as the representative of the type at the realm of runtime values.

\mintinline{haskell}{Proxy}, as its name would suggest, can be used as
singletons. It's a phantom type that could be indexed with any type.

\begin{minted}[xleftmargin=1em]{haskell}
data Proxy t = Proxy
\end{minted}

In the type of \mintinline{haskell}{del}, the type varabile
\mintinline{haskell}{s} would be a \mintinline{haskell}{Symbol} that is decided
 by the argument of type \mintinline{haskell}{Proxy s}.
To use \mintinline{haskell}{del}, we would have to apply it with a clunky
 term-level proxy like this:

\begin{minted}[xleftmargin=1em]{haskell}
del (Proxy :: Proxy "A")
\end{minted}

\section{Making Redis polymorphic}

So far, the datatypes we are dealing with, are all of those built-in Redis data
structures, such as \emph{strings}, \emph{lists (of strings)},
\emph{sets (of strings)}, etc.
But in the real world, these raw strings are hardly useful, people would
usually serialize their data into strings before storing them, and deserialize
them back when in need.

Instead of letting users writing these boilerplates, we will be doing these
serializations/deserializations for them. With the help from
\mintinline{text}{cereal}, a binary serialization library.

\mintinline{text}{cereal} comes with these two functions:
\begin{minted}[xleftmargin=1em]{haskell}
encode :: Serialize a
       => a -> ByteString Source

decode :: Serialize a
       => ByteString -> Either String a
\end{minted}

Which would do all the works for us, as long as the datatype it's handling is
an instance of class \mintinline{haskell}{Serialize}.\footnotemark

\footnotetext{The methods of \mintinline{haskell}{Serialize} will have default
generic implementations for all datatypes with some language extenstions
enabled}

\section{Imposing constraints}

To rule out programs with undesired properties, certain constraints must be
imposed, on what arguments they can take, and what preconditions they must hold.
These constraints are best encoded in types.

\subsection{Redis datatypes}

Redis supports many different datatypes, and most commands only work with
certain types of them. For example: \mintinline{haskell}{SET} with strings or
\mintinline{haskell}{SADD} with sets.

In Edis we implemented five of them.

\subsection{Imposing constraints}

\section{Conclusions and Related Work}
